---
title: "QDNAseq_Exercise"
author: "Minerva"
date: "5/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!requireNamespace("BiocManager", quietly = TRUE))
install.packages("BiocManager")

BiocManager::install("QDNAseq")

#Running QDNAseq
library(QDNAseq)

```

## Adds phenotype data from a file to a QDNAseqReadCounts or a QDNAseqCopyNumbers object.

addPhenodata(object, phenofile) 
metadata or phenotypical data

```{r cars}
library(QDNAseq)
data(LGG150)
readCounts <- LGG150
readCounts <- addPhenodata(readCounts, "phenodata.txt")
```

## Adjusts the filtering on which bins are used.

applyFilters(object, residual=TRUE, blacklist=TRUE, mappability=NA, bases=NA,
chromosomes=c("X", "Y"), verbose=getOption("QDNAseq::verbose", TRUE))

```{r pressure, echo=FALSE}
readCountsFiltered <- applyFilters(readCounts)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
